Enhancing Accelerometer-based Activity Recognition with Capacitive Proximity Sensing

### 2012-06-18 Paper/Paper.tex
typos fixed

Figure \ref{fig:drinking} depicts the data that was recorded for the activity drinking water. The accelerometer data shows that there periodic up- and down-movements while the capacitive proximity sensor delivers data that is associated to the proximity of the table. Figure \ref{fig:making-bread} illustrates the preperation of a bread with marmelade while preparing lunch. It is obvious that the capacitive proximity sensor's data provides valuable information about the distance of the wristband to the table.

@@

We have shown that current wearable inertial sensing devices for activity recognition can be significantly enhanced by integrating a capacitive proximity sensor into the wristband. Regarding the classication accuracy, we obtained an overall increase in correctly classified instances of TODO percent. Some classes, for instance ``preparing bread'' and ``drinking'', could benefit very much from proximity-related sensor data. For such classes the classication performance could be boosted by up to TODO percent.

>>>>

Figure \ref{fig:drinking} depicts the data that was recorded for the activity drinking water. The accelerometer data shows that there periodic up- and down-movements while the capacitive proximity sensor delivers data that is associated to the proximity of the table. Figure \ref{fig:making-bread} illustrates the preparation of a bread with marmalade while preparing lunch. It is obvious that the capacitive proximity sensor's data provides valuable information about the distance of the wristband to the table.

@@

We have shown that current wearable inertial sensing devices for activity recognition can be significantly enhanced by integrating a capacitive proximity sensor into the wristband. Regarding the classification accuracy, we obtained an overall increase in correctly classified instances of TODO percent. Some classes, for instance ``preparing bread'' and ``drinking'', could benefit very much from proximity-related sensor data. For such classes the classification performance could be boosted by up to TODO percent.
